Doing Better Than UCT: Rational Monte Carlo Sampling in Trees

### 2011-06-21 paper/rmcts/paper.tex
paper preparations
eps-greedy regret
added forgotten makefile
paper in progress

\documentclass{article}
\usepackage{algpseudocode}
\usepackage[ruled]{algorithm}
\usepackage{url}
\usepackage{framed}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}

@@

Policies for the Multiarmed Bandit (MB) proved successful for Monte Carlo
tree sampling (MCTS). However, MCTS differs from MB in that only the
final choice, and not all hand pulls, brings a reward.

@@

@@

>>>>

\documentclass{article}
\usepackage{algpseudocode}
\usepackage[ruled]{algorithm}
\usepackage{url}
\usepackage{framed}
\usepackage{amsfonts,amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}

@@

Policies for the Multiarmed Bandit (MB) proved successful for Monte Carlo
tree sampling (MCTS). However, MCTS differs from MB in that only the
final choice, rather than all arm pulls, brings a reward.

@@

\cite{Auer.ucb}

@@

\pagebreak

\appendix

\section{Facts}

{\bf Chernoff bound:} for $m$ independent random variables $X_1, X_2, ..., X_m$
taking values 0 or 1, $X=\sum_{i=1}^m X_i$, and $0\le\delta\le 1$:

\begin{equation}
\label{eq:chernoff-bound}
\Pr[X < (1-\delta)\IE[X]] < e^{-\delta^2\IE[X]/2}
\end{equation}

\section{Finite-time regret bounds}

\subsection{$\varepsilon$-greedy}

Regret $R_\varepsilon$:

\begin{eqnarray}
\IE[R_\varepsilon]&=&\sum_{j=1}^K\Delta_j\Pr(\overline X_j=\max_i\overline X_i)
\end{eqnarray}

For $0<\varepsilon\le1-\frac 1 K$ and $x_0>0$ (see Section 3, Proofs, in \cite{Auer.ucb}):

\begin{eqnarray}
\Pr(\overline X_j=\max_i\overline X_i)&\le&2\left(x_0\cdot \Pr\left\{T_j^R(n)\le x_0\right\} + \frac 2{\Delta_j^2}e^{-\Delta_j^2\lfloor x_0 \rfloor/2}\right)\nonumber\\
&\le&2\left(x_0\cdot \Pr\left\{T_j^R(n)\le x_0\right\} + \frac {2 \cdot
  e^{\Delta_j^2/2}}{\Delta_j^2}e^{-\Delta_j^2 x_0 /2}\right)
\end{eqnarray}

Number of times $\mu$ the $j$th arm is selected {\it randomly}:

\begin{equation}
\mu\triangleq\IE\left[T_j^R(n)\right]=\frac {n\varepsilon} K
\end{equation}

By choosing $x_0=\frac \mu 2$ and applying the Chernoff bound (\ref{eq:chernoff-bound}), obtain:

\begin{eqnarray}
\Pr(\overline X_j=\max_i\overline X_i)&\le& 2\left(\frac {\mu}{2} e^{-\mu/8} + \frac {2e^{\Delta_j^2/2}}{\Delta_j^2}e^{-\Delta_j^2 \mu/4}\right)\nonumber\\
&\le&\left(\mu + \frac {4\sqrt e}{\Delta_j^2}\right)e^{-\Delta_j^2\mu/8}
\end{eqnarray}

\begin{eqnarray}
\IE[R_\varepsilon]&\le&\sum_{j=1}^K\Delta_j\left(\mu + \frac {4\sqrt e}
{\Delta_j^2}\right)e^{-\Delta_j^2\mu/8}\nonumber\\
&\le&K\left(\mu + \frac {4\sqrt e}{\Delta_{\min}}\right)e^{-\Delta_{\min}^2\mu/8}
\end{eqnarray}

\subsection{UCB}

Regret $R_{UCB}$:

\subsection{UVB}

Regret $R_{UVB}$:

\section{Asymptotic bounds for $\varepsilon$-greedy policies}

\section{Case study: $K-1$ and One Arms}
